The Impact of Educational Expenses of New Coders

### 2021-04-18 outputs/paper/paper.Rmd
Add a table for the cleaned dataset

library(tidyverse)
library(dplyr)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
library(kableExtra)
```

@@

# Data
```{r, include=FALSE}
#### TODO's ####
# Explain raw data 
# Discuss the variables
#
```

```{r}
#### Message to Reviewers ####
#
# Code chunks are visible on the PDF for the review.
# Any comments or suggestions are welcome to improve this paper :D
#
# // Variables
# Y: MoneyForLearning
# X: Age, CityPopulation, CommuteTime, Income, MonthsProgramming, SchoolDegree
# c: Gender
#

#### Get data ####
dfNewCoders <- 
  readr::read_csv(here::here("inputs/data/clean_new-coders.csv"))

@@

>>>>

library(tidyverse)
library(dplyr)
library(janitor)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
library(kableExtra)
```

@@

# Data

```{r table1, echo=FALSE, warning=FALSE, message=FALSE}
#### Get data ####
dfNewCoders <- 
  readr::read_csv(here::here("inputs/data/clean_new-coders.csv"))

@@

## Description of Dataset
The original dataset used for this paper is obtained from `freeCodeCamp`’s GitHub page. The format of the dataset is a comma-separated values (CSV) file, which contains 136 columns and 18,175 observations. I selected 8 variables and cleaned the data using the R programming language [@citeR] and the tidyverse package [@cityTidyverse] and the dplyr package [@cityDplyr]. The selected variables are: Age, CityPopulation, CommuteTime, Gender,  Income,  MoneyForLearning,  MonthsProgramming, and SchoolDegree. The CityPopulation is the estimated number of city population of the recipient; the question asked was "About how many people live in your city?”, and there are three options to choose: “less than 100,000”,  "between 100,000 and 1 million", and "more than 1 million". Since these answers were coded as strings, I converted them into numeric variables using the `recode` function of `dplyr` [@cityDplyr]. The answers for CommuteTime and SchoolDegree were also coded as strings in the original dataset, so I applied the same data cleaning process to the variables as I did with CityPopulation. Also, I omitted observations which have a missing value. Table \@ref(tab:tabViewDataset) is a partial view of the cleaned dataset after the preprocessing.

```{r tabViewDataset, echo=FALSE, warning=FALSE, message=FALSE}
#### A partial view of the cleaned dataset ####
tableCleanedData <-
  dfNewCoders[1:10,] %>%
  mutate_all(linebreak) %>%
  kable(caption = "A partial view of \\\\the cleaned dataset",
      booktabs = T,
      escape = F,
      "latex",
      col.names = linebreak(c("Gender", 
                              "Age",
                              "City\nPopulation",
                              "Commute\nTime",
                              "Income",
                              "Months\nProgramming",
                              "School\nDegree",
                              "Money For\nLearning"), align = "c")) %>%
  kable_classic(full_width = F)

tableCleanedData

## Methodology and Data Collection
